---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# textsdc

The goal of textsdc (text statistical data cleaning) is to clean text data statistically. The current version can do:

1. text deduplication using a very simple similarity-based algorithm.

Future version should be able to do:

1. removal of "boilerplates".

Related packages:

1. [quanteda](https://github.com/quanteda/quanteda) - for text analysis
2. [textclean](https://github.com/trinker/textclean) - for normalization of text data

## Installation

You can install the experimental version of textsdc from github:

```{r eval = FALSE}
devtools::install_github("chainsawriot/textsdc")
```

## Example

Calculate the possible duplicates in your input text.

```{r example}
require(textsdc)
demands <- c("Completely withdraw Extradition Bill",
             "Retract the proclamation that protests on 9th June and 12th June were riots",
             "Withdraw criminal charges against all protesters",
             "Thoroughly investigate abuse of powers by the police",
             "Dissolve the Legislative Council by administrative order, and immediately implement Dual Universal Suffrage",
             "Withdraw criminal charges against all protesters",
             "Dissolve the Legisative Council by administrative order, and immediately implement Dual Universal Suffrage")
dups <- calculate_duplication(demands)
dups
```

```{r example2}
dups$dist_matrix
```

Adjust the threshold for duplication.
```{r example3}
dups2 <- calculate_duplication(demands, threshold = 0.9)
dups2
```

Extract the deduplicated version

```{r example4}
get_deduplicated_version(dups2)
```

You can also use percentile-based threshold, e.g. assuming 70% of the articles are not duplicates.

```{r example5}
dups3 <- calculate_duplication(demands, threshold = 0.7, percentile = TRUE)
dups3
```

```{r example6}
get_deduplicated_version(dups3)
```

CJK language

```{r cjk1}
demands2 <- c("徹底撤回修例",
              "收回暴動定義",
              "撤銷對今為所有反送中抗爭者控罪",
              "徹底追究警隊濫權情況",
              "以行政命令解散立法會，立即實行雙真普選",
              "撤銷對今為所有反送中抗爭者控罪",
              "以命令解散立法會，立即實行雙真普選")
dups4 <- calculate_duplication(demands2, threshold = 0.7, percentile = TRUE)
dups4
```

```{r cjk2}
get_deduplicated_version(dups4)
```
