---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```
# textsdc

The goal of textsdc (text statistical data cleaning) is to clean text data statistically. The current version can do:

1. text deduplication using a very simple similarity-based algorithm.

Future version should be able to do:

1. removal of "boilerplates".

Related packages:

1. [quanteda](https://github.com/quanteda/quanteda) - for text analysis
2. [textclean](https://github.com/trinker/textclean) - for normalization of text data

## Installation

You can install the experimental version of textsdc from github:

```{r eval = FALSE}
devtools::install_github("chainsawriot/textsdc")
```

## Example

### Deduplication

Calculate the possible duplicates in your input text.

```{r, eval = FALSE}
require(textsdc)
```

```{r example}
lyrics <- c("He drinks a Whiskey drink",
            "he drinks a Vodka drink",
            "He drinks a Lager drink",
            "he drinks a Cider drink",
            "He sings the songs that remind him of the good times",
            "He sings the songs that remind him of the best times",
            "Oh Danny Boy",
            "Danny Boy",
            "Danny Boy",
            "I get knocked down, but I get up again",
            "You are never gonna keep me down",
            "I get knocked down, but I get up again",
            "You are never gonna keep me down",
            "I get knocked down, but I get up again",
            "You are never gonna keep me down",
            "I get knocked down, but I get up again",
            "You are never gonna keep me down")
dups <- calculate_duplication(lyrics)
dups
```

```{r example2}
dups$dist_matrix
```

Adjust the threshold for duplication.

```{r example3}
dups2 <- calculate_duplication(lyrics, threshold = 0.9)
dups2
```

Extract the deduplicated version

```{r example4}
get_deduplicated_version(dups2)
```

You can also use percentile-based threshold, e.g. assuming 70% of the articles are not duplicates.

```{r example5}
dups3 <- calculate_duplication(lyrics, threshold = 0.7, percentile = TRUE)
dups3
```

```{r example6}
get_deduplicated_version(dups3)
```

CJK language

```{r cjk1}
demands2 <- c("徹底撤回修例",
              "收回暴動定義",
              "撤銷對至今為止所有反送中抗爭者控罪",
              "徹底追究警隊濫權情況",
              "以行政命令解散立法會，立即實行雙真普選",
              "撤銷對至今為止所有反送中抗爭者控罪",
              "解散立法會，立即實行雙真普選")
dups4 <- calculate_duplication(demands2, threshold = 0.7, percentile = TRUE)
dups4
```

```{r cjk2}
get_deduplicated_version(dups4)
```

There are four precedence options on how to get the deduplicated version of the input text.

Default: earlier

```{r earlier}
metallica <- c("The Unforgiven",
               "The Unforgiven II",
               "The Unforgiven III",
               "Fight Fire With Fire",
               "Master of Puppets",
               "For Whom The Bell Tolls",
               "For Whom The Bell Toll",
               "Master of Puppets")
metallica_dups <- calculate_duplication(metallica, threshold = 0.7)
get_deduplicated_version(metallica_dups)
```

Longer

```{r longer}
get_deduplicated_version(metallica_dups, precedence = "longer")
```

Shorter

```{r shorter}
get_deduplicated_version(metallica_dups, precedence = "shorter")
```

Random

```{r random}
get_deduplicated_version(metallica_dups, precedence = "random")
```
